\chapter{Methodology and Equipment}
\label{chap:methodology}
	In order to complete the project a number of methods and materials were used.

<<<<<<< HEAD
In order to complete the project a number of methods and materials were used.
\section{Methodology}
\label{sec:methodology}
The workload in this project can be divided into PCB-design, manufacturing and high- and low-level programming. Since the workload is large in the low-level programming all multiple people were working on it. Whereas the workload for the other parts were mainly distributed to individuals, to maximize resource utility.   

\subsection{PCB Design and manufacturing}
The design for PCB with the piezo electric elements were conducted by first doing some research on the working principles of the piezo. Since it turn out to be rather hard to theoretically design the PCB  a more pragmatic approach were conducted. 
The sensor characteristics were analyzed by mounting it with a big potentiometer in parallel and measuring the generated voltage when hitting the base plate with a ping pong ball.
Based on this analysis a prototype where put together and tested on a breadboard. 
Then the design from the breadboard are drawn as a schematics and a board in eagle. 
After verifying the schematics and board one of the four identical PCB's are manufactured and tested before producing the others.
Other simpler electrical connections are manufactured on stripboards to minimize time spend on producing PCB's.

\subsection{Low-level programming}
=======
	\section{Methodology}
	\label{sec:methodology}
		The whole project can be divided in four parts that will be treat separately, being this: $mechanics$, $electronics$, $programming$ and $computer program$. At the same time this tasks were organized so:

		In the mechanics part the schedule was:
		\begin{itemize}
			\item Design of the structure
			\item Manufacturing of the laser cutter machine parts
			\item Manufacturing of the 3D printed parts
			\item Structure assembly
			\item Add sensors and electronics to the whole structure
		\end{itemize}

		In turn, the electronics part:
		\begin{itemize}
			\item Circuit design
			\item First prototype test in breadboard
			\item Manufacturing of the PCB boards
			\item Testing
		\end{itemize}
>>>>>>> origin/master

		Whereas in the programming part:
		\begin{itemize}
			\item \textcolor{red}{Blabla}
		\end{itemize}

<<<<<<< HEAD
\subsection{High-level programming}


\subsection{Design and manufacturing of mechanical part}
=======
		To finish, the computer program was divided in:
		\begin{itemize}
			\item UI conceptualization
			\item Serial research and first test
			\item Develop of the whole program
			\item Testing
		\end{itemize}

	\section{Equipment}
	\label{sec:equipment}
		To develop and test the designed solution the following equipments were used.
		\begin{itemize}
			\item Oscilloscope
			\item Multimeter
			\item Soldering iron
			\item \textcolor{red}{FPGA Spartan 3??}
			\item Eagle 7.1 Light
			\item Breadboard
			\item PCB development instruments
			\item Printer
			\item DC servo motor
			\item Murata piezo sensor 7BB-20-6L0
			\item 3D printer
			\item Laser cutter machine
		\end{itemize}
>>>>>>> origin/master
